---
title: "teens-and-tech-2018"
author: "Monique McLeary"
date: "2/5/2022"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(tidyverse)
# library(kableExtra)


data <- read_xlsx("clean-teens-tech-data.xlsx")

```

### Background

The Teens and Tech survey was administered in 2018. Click [here](https://www.pewresearch.org/internet/dataset/teens-and-tech-survey-2018/) to access the data and view published reports from Pew Research.


### Demographics

First, I want to take a look at who the survey respondents are. Let's start with gender:

```{r gender, echo=F}

gender_table <- data %>% 
  select(71:82) %>% 
  mutate(GENDER = ifelse(GENDER==1, "male", "female")) %>% 
  group_by(GENDER) %>% tally() %>% 
  mutate(percent = round(100*(n/sum(n)),2)) 
  

gender_table
```

There are slightly fewer female respondents than male - the difference is slightly more pronounced than I expected it to be. Besides gender, I am unable to deduce any of the other demogrpahic variable coding schemes. I'll have to continue exploring, or maybe I could request a detailed codebook.

```{r echo=F}

gender <- data %>% 
  select(FRIEND2, FRIEND3, 71:82) %>% 
  mutate(friends_online = ifelse(FRIEND2==1, "Everyday or almost every day", 
                          ifelse(FRIEND2==2, "Several times a week", 
                                 ifelse(FRIEND2==3, "About once a week", "Less often")))) %>% 
  mutate(GENDER = ifelse(GENDER==1, "male", "female")) %>% 
  ggplot(aes(friends_online, fill=GENDER))+
           geom_histogram(stat = "count", position = "dodge")

gender
```

```{r echo=F}

time_inperson <- data %>% 
  select(FRIEND2, FRIEND3, 71:82) %>% 
  mutate(time_in_person = ifelse(FRIEND3==1, "Too much",
                                 ifelse(FRIEND3==2, "Too little", "About the right amount"))) %>% 
  mutate(friends_online = ifelse(FRIEND2==1, "Everyday or almost every day", 
                          ifelse(FRIEND2==2, "Several times a week", 
                                 ifelse(FRIEND2==3, "About once a week", "Less often")))) %>% 
  ggplot(aes(friends_online, fill=time_in_person))+
           geom_histogram(stat = "count", position = "dodge")

time_inperson
```

